draft final Project

### 2021-04-26 draft_writing.Rmd
draft_recommit

## EXPLORATORY ANALYSIS
In order to better understand the elephant trail data, we used exploration methods to examine these data and their relationship to one another. First, we wanted to see the total amount of trails for each use type (P, M, W) in order to see which type of trail was most present. By summarizing the total amounts of each use of trail, we were able to see the Poor trails were the most commonly described trail.

@@

Visualizing these trails was helpful to explore these data spatially. To do this, we used mapview to get an idea of where the trails are located and the type of condition the elephants were traveling on. Given the size of the dataset, we created a subset to just look at one date where all three trail types were present. On April 15, 2018, all three trails were documented which made this a good date to further examine.

>>>>

## EXPLORATORY ANALYSIS
The elephant trail dataset has dimensions of 40,910 observation and 11 variables. We looked primarily at the use and the width of each trail and the longitude and latitude. First, we wanted to see the total amount of trails for each use type (P, M, W) in order to see which type of trail was most present. By summarizing the total amounts of each use of trail, we were able to see the Poor trails were the most commonly described trail.

@@

Visualizing these trails was also helpful to explore these data spatially. To do this, we used mapview to get an idea of where the trails are located and the type of condition the elephants were traveling on. Given the size of the dataset, we created a subset to just look at one date where all three trail types were present. On April 15, 2018, all three trails were documented which made this a good date to further examine.
